### 2021-07-07 supp.tex
updating

>>>>

\subsection{Measuring relative growth for multiple co-circulating strains}

In order to model multiple co-circulating strain, we write $i_x(t)$ to represent the incidence of strain $x$ (for $x = 1, \dots, N$).
When incidence is changing exponentially ($i_x(t) = i_x(t_0) \exp(r_x t)$), the proportion of strain $y$ in the population can be written as:
\begin{equation}
p_y(t) = \frac{i_y(t_0) \exp(r_y t)}{\sum_{x=1}^N i_x(t_0) \exp(r_x t)}.
\end{equation}
Logit transforming $p_y(t)$ then gives:
\begin{align}
\mathrm{logit}(p_y(t)) &= \log\left(\frac{p_y(t)}{1-p_y(t)}\right)\\
&= \log\left(\frac{i_y(t_0) \exp(r_y t)}{\sum_{x \neq y} i_x(t_0) \exp(r_x t)}\right)\\
&= \log(i_y(t_0)) + r_y t - \log \left(\sum_{x \neq y} i_x(t_0) \exp(r_x t)\right)
\end{align}
which is a nonlinear function of time $t$.
Therefore, the growth rate measured at the logit scale is expected to change over time when multiple strains are co-circulating. 
Instead, a multinomial logistic regression model is required to infer relative speed \citep{campbell2021increased}.
